### 2014-06-13 scratchwork/makenew.mixEM.Rmd
fixing dropbox merge issue

penloglik = function(pi, matrix_lik, prior){
  m  = t(pi * t(matrix_lik)) # matrix_lik is n by k; so this is also n by k
  m.rowsum = rowSums(m)
  loglik = sum(log(m.rowsum))
  subset = (prior-1) != 0
  priordens = sum((prior-1)[subset]*log(pi[subset]))
  return(loglik+priordens)
}

mixEM2 = function(matrix_lik, prior, pi.init = NULL,tol=1e-7, maxiter=5000){
  if(is.null(pi.init)){
    pi = rep(1/k,k)# Use as starting point for pi
  } 
  res = squarem(par=pi.init,fixptfn=fixpoint, objfn=penloglik,matrix_lik=matrix_lik, prior=prior, control=list(maxiter=maxiter,tol=tol))
  return(list(pihat = res$par, B=res$value.objfn, 
              niter = res$iter, converged=res$convergence))
}

#as above but with initial iterations done with smaller sample sizes
#and tolerance set according to sample size
mixEM3 = function(matrix_lik, prior, pi.init = NULL,tol=1e-7, maxiter=5000){
  if(is.null(pi.init)){
    pi = rep(1/k,k)# Use as starting point for pi
  } 
  n = nrow(matrix_lik)
  if(n>1000){       
    res = squarem(par=pi.init,fixptfn=fixpoint, objfn=penloglik,matrix_lik=matrix_lik[1:1000,], prior=prior, control=list(maxiter=maxiter,tol=1e-3,trace=TRUE))
    pi.init = res$par
    print(pi.init)
  }
  res = squarem(par=pi.init,fixptfn=fixpoint, objfn=penloglik,matrix_lik=matrix_lik, prior=prior, control=list(maxiter=maxiter,tol=tol,trace=TRUE))
  return(list(pihat = res$par, B=res$value.objfn, 
              niter = res$iter, converged=res$convergence))
}
```

>>>>

negpenloglik = function(pi, matrix_lik, prior){
  m  = t(pi * t(matrix_lik)) # matrix_lik is n by k; so this is also n by k
  m.rowsum = rowSums(m)
  loglik = sum(log(m.rowsum))
  subset = (prior-1) != 0
  priordens = sum((prior-1)[subset]*log(pi[subset]))
  return(-(loglik+priordens))
}

mixEM2 = function(matrix_lik, prior, pi.init = NULL,tol=1e-7, maxiter=5000){
  if(is.null(pi.init)){
    pi = rep(1/k,k)# Use as starting point for pi
  } 
  res = squarem(par=pi.init,fixptfn=fixpoint, objfn=negpenloglik,matrix_lik=matrix_lik, prior=prior, control=list(maxiter=maxiter,tol=tol))
  return(list(pihat = res$par, B=res$value.objfn, 
              niter = res$iter, converged=res$convergence))
}

#as above but with initial iterations done with smaller sample sizes
#and tolerance set according to sample size
mixEM3 = function(matrix_lik, prior, pi.init = NULL,tol=1e-7, maxiter=5000){
  if(is.null(pi.init)){
    pi = rep(1/k,k)# Use as starting point for pi
  } 
  n = nrow(matrix_lik)
  if(n>1000){       
    res = squarem(par=pi.init,fixptfn=fixpoint, objfn=negpenloglik,matrix_lik=matrix_lik[1:1000,], prior=prior, control=list(maxiter=maxiter,tol=1e-3,trace=TRUE))
    pi.init = res$par
    print(pi.init)
  }
  res = squarem(par=pi.init,fixptfn=fixpoint, objfn=negpenloglik,matrix_lik=matrix_lik, prior=prior, control=list(maxiter=maxiter,tol=tol,trace=TRUE))
  return(list(pihat = res$par, B=res$value.objfn, 
              niter = res$iter, converged=res$convergence))
}
```

### 2014-06-13 scratchwork/test.turboem.Rmd
fixing dropbox merge issue

penloglik = function(pi, matrix_lik, prior){
  m  = t(pi * t(matrix_lik)) # matrix_lik is n by k; so this is also n by k
  m.rowsum = rowSums(m)
  loglik = sum(log(m.rowsum))
  priordens = sum((prior-1)*log(pi))
  return(loglik+priordens)
}

@@

```{r}
  library(turboEM)
  res = turboem(par=pi.init, control.run=list(convtype = "objfn",tol=1e-5),fixptfn=fixpoint, objfn=penloglik, pconstr=pconstr,method=c("em", "squarem", "pem","decme","qn"), matrix_lik=lik,prior=prior)
  options(digits=13)
  res
  library(devtools)
  devtools::load_all("../package/ashr")
  system.time(res2<-mixEM(lik, prior, pi.init))
  length(res2$B)
  res2$B[length(res2$B)]
```

>>>>

negpenloglik = function(pi, matrix_lik, prior){
  m  = t(pi * t(matrix_lik)) # matrix_lik is n by k; so this is also n by k
  m.rowsum = rowSums(m)
  loglik = sum(log(m.rowsum))
  priordens = sum((prior-1)*log(pi))
  return(-(loglik+priordens))
}

@@

```{r}
  library(turboEM)
  res = turboem(par=pi.init, control.run=list(convtype = "objfn",tol=1e-5),fixptfn=fixpoint, objfn=negpenloglik, pconstr=pconstr,method=c("em", "squarem", "pem","decme","qn"), matrix_lik=lik,prior=prior)
  options(digits=13)
  res
  library(devtools)
  devtools::load_all("../package/ashr")
  system.time(res2<-mixEM(lik, prior, pi.init))
  length(res2$B)
  res2$B[length(res2$B)]
```
